### 2024-05-08 Text/Thesis/chapters/2_background.tex
doctoral qualification document

\subsection{Remote Sensors}
Remote sensors remotely collect data by measuring the electromagnetic (EM) radiation at specific spectral ranges (usually called bands). 
When they are deployed on satellites or mounted on aircraft, they are called spaceborne and airborne remote sensors, respectively.
 Spaceborne remote sensors orbit the Earth at heights of 500 to 800 km~\citep{everaerts2005pegasus}, providing data in a wide range of ground resolutions, and at various polarizations and radar bands.

@@

In large, optical sensors can be classified, by the number of spectral bands which they image, into hyperspectral, multispectral, and panchromatic sensors. 
Whereby hyperspectral sensors image the full optical subsection of the EM-spectrum into hundreds of narrow spectral bands, while panchromatic sensors image the visible light spectrum using a single, wide spectral band~\citep{Sara2021}.
Similarly, SAR sensors can also be classified based on their operational bandwidth into C, L and X-band, with L-band being the lowest frequency and thus the highest level of vegetation and soil penetration.
However, due to the relationship between wave-length and spatial resolution present in SAR imagery~\citep{cumming2005digital}, X-band imagery exhibits the highest spatial resolution and thus provides the detailed information about surface structure. 
In optical imagery, a similar trade-off exists, except it is between spatial resolution and spectral resolution. 
Due to data storage and throughput constraints hyperspectral and multispectral images tend to have a lower resolution than panchromatic imagery.

>>>>

\subsection{Remote Sensors}
Remote sensors collect data remotely by measuring electromagnetic (EM) radiation within specific spectral ranges,  often called bands. 
When they are deployed on satellites or mounted on aircraft, they are called spaceborne and airborne remote sensors, respectively.
 Spaceborne remote sensors orbit the Earth at heights of 500 to 800 km~\citep{everaerts2005pegasus}, providing data in a wide range of ground resolutions, and at various polarizations and radar bands.

@@

In general, optical sensors can be classified by the number of spectral bands they image into hyperspectral, multispectral, and panchromatic sensors. 
Hyperspectral sensors image the full optical subsection of the EM spectrum into hundreds of narrow spectral bands, while panchromatic sensors image the visible light spectrum using a single, wide spectral band~\citep{Sara2021}.
Similarly, SAR sensors can also be classified based on their operational bandwidth into C, L and X-band, with L-band being the lowest frequency and thus the highest level of vegetation and soil penetration.
However, due to the relationship between wave-length and spatial resolution present in SAR imagery~\citep{cumming2005digital}, X-band imagery exhibits the highest spatial resolution and thus provides the detailed information about surface structure. 
In optical imagery, a similar trade-off exists, except it is between spatial resolution and spectral resolution. 
Due to data storage and throughput constraints hyperspectral and multispectral images tend to have a lower resolution than panchromatic imagery.
